Palaeodistribution of crop progenitors and wild foods in the Southern Levant

### 2023-08-15 analysis/analysis.Rmd
Tidy predictions

# Fit to each taxon
occ |>
  nest(.by = taxon) |>
  mutate(
    data = map(data, as_tibble),
    fit = map(data, \(data) {
      fit(rf_model, factor(present) ~ ., data = select(data, rf_pred_vars()))
    })) ->
  rf_fits
```

@@

```{r predict}
# TODO: tidy
# TODO: parallelise
rf_fit <- filter(rf_fits, taxon == "Secale cereale") |>
  pull(fit)[[1]]

# TODO: predict on all periods (maybe combine stars and collapse into dimension first?)
rf_pred_cur <- predict(climate$cur, rf_fit, type = "prob")
rf_pred_eh <- predict(climate$EH, rf_fit, type = "prob")
rf_pred_yds <- predict(climate$YDS, rf_fit, type = "prob")
rf_pred_ba <- predict(climate$BA, rf_fit, type = "prob")
rf_pred_hs1 <- predict(climate$HS1, rf_fit, type = "prob")
rf_pred_lgm <- predict(climate$LGM, rf_fit, type = "prob")

rf_pred <- c(rf_pred_cur, rf_pred_eh, rf_pred_yds, rf_pred_ba, rf_pred_hs1,
             rf_pred_lgm)
names(rf_pred) <- c("cur", "EH", "YDS", "BA", "HS1", "LGM")

>>>>

# Fit to each taxon
# TODO: parallelise
occ |>
  nest(.by = taxon) |>
  mutate(
    data = map(data, as_tibble),
    fit = map(data, \(data) {
      fit(rf_model, factor(present) ~ ., data = select(data, rf_pred_vars()))
    })) ->
  rf_fits
```

@@

```{r predict}
# TODO: tidy
rf_fit <- filter(rf_fits, taxon == "Triticum urartu") |>
  pull(fit)
rf_fit <- rf_fit[[1]]

# TODO: Maybe combine stars and collapse period into dimension first?
rf_pred <- map(climate, predict, model = rf_fit, type = "prob")
rf_pred <- map(rf_pred, \(x) x[".pred_TRUE"])
rf_pred <- do.call(c, rf_pred)
rf_pred <- st_redimension(rf_pred, name = "period")
